Hybrid Threads for the Parrot Virtual Machine

### 2012-02-23 Paper.tex
More on GC design

>>>>

Since cross threaded writes are already forbidden and all read access to other thread's data goes through the very narrow channel of proxy objects, forcing a complete separation of the thread's memory domains was only a small step. By having separate memory areas for each interpreter, it became possible to have each interpreter to run its own garbage collector. This way, the known to work single threaded GC implementation could be continued to be used.

Separation of memory domains is a problem for objects which are only referenced from other threads. But since all objects which could be accessed from other threads have to be pushed onto the Task object representing such threads, they can still be referenced from there.
